\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE Sachin Maniyar} \\ 
    \begin{multicols}{2}
    \begin{flushleft}
    \href{https://www.linkedin.com/in/sachin-maniyar}{\faLinkedinSquare}
    
    \end{flushleft}
    
    \begin{flushright}
    
    \href{mailto:{your email adress}}{sachinmaniyar3@gmail.com}\\
    \href{{Phone Number: }}{+91 7990505920}\\

    \end{flushright}
    \end{multicols}
\end{center}

%-----------CAREER SUMMARY-----------

    \small{DevOps Engineer with \textbf{3.3 Years} of experience, proficient in AWS, Docker, Kubernetes, CI/CD pipelines, and
automation.Skilled in creating infrastructure as code using CloudFormation Templates (CFT).Extensive experience in designing and managing infrastructure on AWS, utilizing a wide range of services such as EC2, S3, RDS, ECR, ECS, lambda, and more.Proficient in Python programming and Boto3 library, automating AWS tasks.Strong understanding of network security principles, including the design of secure VPC
architectures, enforcement of access controls using Security Groups (SG), and ensuring data
privacy and compliance.}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages Known}{: Python, Groovy, Shell Scripting, Yaml  \\
        \vspace{2pt}
        \textbf{Automation/Build}{: Jenkins, Maven, JFrog, SonarQube} \\
        \vspace{2pt}
        \textbf{IAC}{: CloudFormationTemplates } \\
        \vspace{2pt}
        \textbf{Containerization}{: Docker, Kubernetes } \\
        \vspace{2pt}
        \textbf{Cloud Services}{: AWS - IAM, S3, EC2, VPC, ECR, R53, ApiGateway, RDS, Batch}\\
        \vspace{2pt}
        \textbf{Version Control}{: Git, GitHub, Bitbucket, Gitlab}\\
        \vspace{2pt}
        \textbf{Tools}{: JIRA, SharePoint, Confluence, Databricks, Snowflake}\\
        \vspace{2pt}
        \textbf{Operating Systems}{: Windows, Linux}\\
        \vspace{2pt}
        \textbf{Monitioring}{: CloudWatch, CloudTrial} \\
    }}
}
\end{itemize} 

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    
    \resumeSubheading
      {DevOps Engineer at Cognizant [Nov. 2020 - Present]}{Bangalore, Karnataka}
      {}{}
      \resumeItemListStart
         
         \resumeItem{Implemented a Jenkins pipeline using Groovy scripting to automate the build, test, and
deployment process for a cloud-native application.}
         \resumeItem{Worked on creating docker file and pushing images to private repository.}
         \resumeItem{Developed and executed AWS CLI scripts for automating infrastructure provisioning,
configuration, and maintenance tasks.}
         \resumeItem{Managed AWS account and hands-on experience in IAM, S3, Lambda, VPC, R53, Secrets
Manager, ECR,ECS, Security Groups etc.}
         \resumeItem{Designed and deployed CloudFormation templates for infrastructure provisioning, enabling
consistent and repeatable deployments.}
         \resumeItem{Utilized the Boto3 library to programmatically interact with AWS services, retrieve resource
information, and perform actions based on specific conditions or triggers.}
         \resumeItem{Assisted in the deployment and management of containerized applications on Kubernetes
clusters, gaining exposure to key concepts such as pods, deployments, services, and ingress
controllers.}
        \resumeItem{Deployed a Dockerized application on AWS ECS, leveraging ECR for image storage and AWS
Batch for batch processing tasks.}
         \resumeItem{Access management in Snowflake and Databricks. Worked with Snowflake tool for warehouse
provision, table permission to users and secrets to connect to database.}
         \resumeItem{Was involved in multiple troubleshooting calls and helped team with the resolution.}
         \resumeItem{Active participation in knowledge sharing sessions.}

    \resumeItemListEnd

%-----------EDUCATION-----------

\section{Education}

  \item{
        \textbf{{B.E. in Information Technology [2016-2020]}}\\
        \resumeItemListStart
        \resumeItem{Government Engineering College, Gandhinagar [GTU] – 7.77 CGPA}
        
        \resumeItemListEnd
        
        \textbf{{H.S.C. [2016]}}\\
        \resumeItemListStart
        \resumeItem{Modi Schools, Rajkot [GHSEB] – 85\%}
        \resumeItemListEnd
        \vspace{2pt}
        \textbf{{S.S.C. [2014]}}
        \resumeItemListStart
        \resumeItem{St Marry’s School, Gondal [GSEB] – 75\%}
        \resumeItemListEnd
        \vspace{2pt}
        }
%-----------Awards & Recognition-----------
\section{Awards \& Recognition}


      \resumeItemListStart
         
         \resumeItem{Received top rating for my contributions to project.}
         \resumeItem{Received good feedback from client for the timely delivery and project execution.}
         \resumeItem{Leading team of 10 colleagues for the tower solution.}

    \resumeItemListEnd
      

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{

     {
      \href{https://www.credly.com/badges/8f347325-108c-40a7-9478-87894782534a/public_url}{\textbf{AWS Certified Cloud Practitioner CLF-C02}}
    
    }}



 \end{itemize}


    
\end{document}
